Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-19 paper/snakemajoranas.tex
new abstract

\date{\today}
\begin{abstract}
Quasi-particle trajectories in high density SNS junctions that have a large momentum parallel to the junction have a very long flight time.
These trajectories that do not encounter the superconductor for a long time weaken the proximity effect in Josephson junctions.
This results in a very small induced gap and a soft gap in Majorana devices.
We propose to eliminate these long trajectories using a new Majorana device.
We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with a gap increased by more than an order of magnitude and a significantly reduced Majorana decay length.
Additionally, we show that to exploit the benefits of this system, the details exact of the geometry are not important.
\end{abstract}

>>>>

\date{\today}
\begin{abstract}
Quasi-particle trajectories in high density superconductor-semiconductor-superconductor junctions that have a large momentum parallel to the junction have a very long flight time, and therefore a small induced superconducting gap.
Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to low electron density.
We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with both the gap and the Majorana size improved by more than an order of magnitude for realistic parameters.
In addition to the improved robustness of Majoranas, this new zigzag geometry is insensitive to the geometric details and the device tuning.
\end{abstract}
